---
title: "O1NAEX Exercise 06"
author: "Tereza Fucsiková"
date: "2023-11-06"
output:
  html_document:
    df_print: paged
  pdf_document: default
editor_options:
  markdown:
    wrap: 72
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
list_of_packages <- c("tidyverse","MASS",'FrF2', "metR", "geoR") # "agricolae","nortest","lattice","pwr",
missing_packages <- list_of_packages[!(list_of_packages %in% installed.packages()[,"Package"])]
missing_packages
if(length(missing_packages)) install.packages(missing_packages)
lapply(list_of_packages, library, character.only = TRUE)
```



## Problem 6.31 + 6.32

from the chapter 6, D. C. Montgomery DAoE - 8. edition.

An experiment was conducted on a chemical process that produces a
polymer. The four factors studied were temperature (A), catalyst
concentration (B), time (C), and pressure (D). Two responses, molecular
weight and viscosity, were observed. The design matrix and response data
are following:

```{r}
df631 <- read.table("https://raw.githubusercontent.com/francji1/01NAEX/main/data/Problem_6_31.txt",header=TRUE,sep=";")
(df631)
```

Use only first sixteen measurements, center points will be covered in
the following lesson.

## Tasks:

1.Consider only the molecular weight response. Plot the effect 
estimates on a normal probability scale. What effects appear
important?

2.Use an analysis of variance to confirm the results from the first 
part.

3.Write down a regression model to predict molecular weight as a
  function of the important variables.
  
4.Analyze the residuals and comment on model adequacy.

5.Repeat parts 1.--4. using the viscosity response.


Use the regression models for molecular weight and viscosity to answer
the following questions. 

6.Construct a response surface contour plot
for molecular weight. In what direction would you adjust therocess
variables to increase molecular weight? 

7. Construct a response surface
contour plot for viscosity. In what direction would you adjust the
process variables to decrease viscosity? 

8. What operating conditions
would you recommend if it was necessary to produce a product with
molecular weight between 2400 and 2500 and the lowest possible
viscosity?

```{r}
m         <-  FrF2(2^4, 4, replications = 1, randomize = F,factor.names = c("A", "B","C", "D"))
Weight    <- df631[1:16,"Weight"]
Viscosity <- df631[1:16,"Viscosity"]
m_full <-m
m_full         <- add.response(m_full,Weight)
m_full         <- add.response(m_full,Viscosity)


response.names(m_full)
m_full
```

## Tasks:

1.  Consider only the molecular weight response. Plot the effect
    estimates on a normal probability scale. What effects appear
    important?

```{r}
m_weight <- m
m_weight <- add.response(m_weight,Weight)

response.names(m_weight)
m_weight
```

```{r}
lm_coeffs_1 <- lm(Weight ~ A * B * C * D - A:B:C:D, data=m_full)
effects_1 <-as.data.frame(2*lm_coeffs_1$coefficients)
names(effects_1)[1] <- 'Effects'
print(effects_1)
```

```{r}
# Daniel plot
qqplot(DanielPlot(m_weight,alpha=0.1)$x,DanielPlot(m_weight, alpha=0.1)$y)
qqline(DanielPlot(m_weight,alpha=0.1)$y)
```
The interactions A, C and A:B appear to be important.



2.  Use an analysis of variance to confirm the results from the first
    part.

```{r}
summary(aov(Weight ~ A + C + A:B, data=m_full))
```
It confirms the result from the first part that A, C, AB are
significant.



3.  Write down a regression model to predict molecular weight as a
    function of the important variables.

```{r}
model_weight_reg <- lm(Weight ~ A + C + A:B, data=m_full)
summary(model_weight_reg)
```
As a result: molecular weight = 2506.25 + 61.875\*A + 100.625\*C +
60\*A\*B.



4.  Analyze the residuals and comment on model adequacy.

```{r}
# Normal Probability Plot of Residuals
qqnorm(residuals(model_weight_reg))
qqline(residuals(model_weight_reg))

# Residuals vs. Predicted Values Plot
plot(fitted(model_weight_reg), residuals(model_weight_reg), 
     xlab = "Predicted Values", ylab = "Residuals",
     main = "Residuals vs. Predicted Values")
abline(h = 0, col = "red")

```
There is one outlier that should be investigated.



5.  Repeat parts 1.--4. using the viscosity response.

```{r}
m_viscosity <- m
m_viscosity <- add.response(m_viscosity,Viscosity)

response.names(m_viscosity)
m_viscosity
```

```{r}
lm_coeffs_2 <- lm(Viscosity ~ A * B * C * D - A:B:C:D, data=m_full)
effects_2 <-as.data.frame(2*lm_coeffs_2$coefficients)
names(effects_2)[1] <- 'Effects'
print(effects_2)
```

```{r}
# Daniel plot
qqplot(DanielPlot(m_viscosity,alpha=0.1)$x,DanielPlot(m_viscosity, alpha=0.1)$y)
qqline(DanielPlot(m_viscosity,alpha=0.1)$y)
```

The interactions A, B appear to be important.

```{r}
summary(aov(Viscosity ~ A + B, data = m_full))
```
It confirms the result from the first part that A and B are significant.



```{r}
model_viscosity_reg <- lm(Viscosity ~ A + B, data=m_full)
summary(model_viscosity_reg)
```
As a result: viscosity = 1500.625 + 48.125\*A + 45.625\*B.



```{r}
# Normal Probability Plot of Residuals
qqnorm(residuals(model_viscosity_reg))
qqline(residuals(model_viscosity_reg))

# Residuals vs. Predicted Values Plot
plot(fitted(model_viscosity_reg), residuals(model_viscosity_reg), 
     xlab = "Predicted Values", ylab = "Residuals",
     main = "Residuals vs. Predicted Values")
abline(h = 0, col = "red")

```
There is one outlier that should be investigated.




Use the regression models for molecular weight and viscosity to answer
the following questions.

6.  Construct a response surface contour plot for molecular weight. In
    what direction would you adjust therocess variables to increase
    molecular weight?

7.  Construct a response surface contour plot for viscosity. In what
    direction would you adjust the process variables to decrease
    viscosity?

```{r}
data <- df631[-c(17,18,19,20),]
data
```

```{r}
p.lm1 <- lm(Weight ~ Temperature + Concentration + Time + Temperature:Concentration, data = data)
p.lm2 <- lm(Viscosity ~ Temperature + Concentration, data = data)
```

```{r}
p.tmp <- list(Temperature = seq(100, 120, by=1), Concentration = seq(4, 8, by = 1))
p.new.data <- expand.grid(p.tmp)
p.new.data$Time <- 24
p.new.data$fit <- predict(p.lm1, p.new.data)

p.new.data2 <- p.new.data
p.new.data2$fit <- predict(p.lm2, p.new.data)
p.new.data$response = "Weight"
p.new.data2$response = "Viscosity"
p.data = rbind(p.new.data, p.new.data2)

p.new.data3 <- p.new.data2 %>%
  mutate(fit2 = predict(p.lm1, p.new.data)) %>%
  dplyr::select(-response) %>%
  dplyr::rename(Viscosity = fit, 
        Weight = fit2)

p.new.data3
```

```{r}
g <-ggplot(p.new.data3, aes(Temperature, Concentration)) +
  geom_contour(aes(z = Viscosity), col = "red", binwidth = 10) +
  geom_contour(aes(z = Weight), col = "blue", binwidth = 10) +
  geom_text_contour(aes(z = Viscosity), col = "red") +
  geom_text_contour(aes(z = Weight), col = "blue")
g
```
Blue = Weight: To increase molecular weight I would increase the
temperature, catalyst concentration and time. Red = Viscosity: To
decrease viscosity I would decrease the temperature and catalyst
concentration.




8.  What operating conditions would you recommend if it was necessary to
    produce a product with molecular weight between 2400 and 2500 and
    the lowest possible viscosity?

```{r}
filtered_data <- p.new.data3 %>%
  filter(Weight >= 2400, Weight <= 2500) %>%
  filter(Viscosity == min(Viscosity))

recommended_conditions <- filtered_data %>%
  dplyr::select(Temperature, Concentration, Time, Weight, Viscosity)

print(recommended_conditions)
```
